Twisted eleven-dimensional supergravity

### 2021-11-04 nonmin.tex
G2

We have provided numerous consistency checks that the eleven-dimensional theory defined on a manifold with $SU(5)$ holonomy is a twist of supergravity. 
We have referred to this theory as minimal as it depends on the complex structure in the maximal number of directions. 
In this section we characterize a further twist of eleven-dimensional supergravity from the lens of the holomorphic theory.  
This further twist is invariant for the group $G_2 \times SU(2)$ and is topological along seven directions, as opposed to just a single direction as in the $SU(5)$ twist.

On flat space, the further twist is essentially unique and renders the theory topological in seven directions, rather than just one as in the holomorphic twist. 
We will show that it is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory. 
In the BV formalism, the theory $\ZZ/2$ graded and has fields given by
\[
A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
\]
where $\Pi$, as always, denotes parity shift.
The equations of motion are of the form
\[
\dbar A + \d_{\RR^7} A + \partial_{z_1} A \wedge \partial_{z_2} A = 0 .
\]
The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
We give a precise definition below.

>>>>

We have provided numerous consistency checks that the eleven-dimensional theory defined on a manifold with $SU(5)$ holonomy is a twist of supergravity. 
We have referred to this theory as ``minimal,'' since it renders the minimal number of translations homotopically trivial, or (slightly improperly) as ``holomorphic.''
In this section we characterize the unique further twist of eleven-dimensional supergravity on flat space, as seen through the lens of the holomorphic theory.  
This further twist is invariant for the group $G_2 \times SU(2)$ and is fully topological along seven directions, as opposed to just a single direction as in the minimal twist. This is easiest to see by decomposing the eleven-dimensional spinor as a representation of $\Spin(4) \times \Spin(7)$; from this perspective, a square-zero element is a rank-one element in the tensor product of a chiral spin representation of~$\Spin(4)$ and the spin representation of~$\Spin(7)$. Elements of the latter fall into two distinct orbits under the $\Spin(7)$ action, the minimal orbit---``Cartan pure spinors''---and the generic orbit~\cite{Igusa}. The stabilizer of an element of the generic orbit is~$G_2$, almost by definition.

We will show that the non-minimal twist is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory, using a direct description of the further twist together with an indirect cohomological argument. This confirms a conjecture in the literature~(\cite{CostelloM5}; see also~\cite{RY}).

In the BV formalism, the theory is $\ZZ/2$ graded, with fields given by
\[
A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
\]
where $\Pi$, as always, denotes parity shift.
The equations of motion are of the form
\[
\dbar A + \d_{\RR^7} A + \partial_{z_1} A \wedge \partial_{z_2} A = 0 .
\]
The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
We give a precise definition below.
